results

### 2020-10-27 analysis/results.Rmd
facetted subject view

@@

```{r}
field_funder <- hybrid_df %>%
  filter(oa_sponsor_type == "FundingBody") %>% 
  left_join(funder_codes, by = c("oa_sponsor_name"="oa_sponsor")) %>% 
  mutate(oa_sponsor = ifelse(is.na(oa_sponsor_short), "Other", oa_sponsor_short)) %>%
  mutate(oa_sponsor = fct_infreq(oa_sponsor)) %>%
  mutate(oa_sponsor = fct_lump_n(oa_sponsor, 10)) %>%
  left_join(jn_subjects, by = "issn") %>%
  filter(!is.na(top_level), top_level != "Multidisciplinary") %>%
  group_by(oa_sponsor, top_level) %>%
  summarise(n_oa_type = n_distinct(doi)) %>%
  mutate(prop = n_oa_type / sum(n_oa_type)) %>%
  mutate(oa_sponsor = fct_relevel(oa_sponsor, "Other", after = Inf))
ggplot(field_funder, aes(x = factor(oa_sponsor), 
                         y = reorder(top_level, desc(top_level)), 
                         colour = prop, size = n_oa_type)) + 
  geom_point() +
  scale_color_viridis_c(labels = scales::percent_format(accuracy = 5L),
                      option = "magma",
                      name = "Percentage per funder",
                      breaks =  scales::extended_breaks()) +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 6), position = "top") +
  labs(x = NULL, y = NULL) +
  theme_minimal_grid(font_size = 10) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank()) +
  theme(legend.position = "top", legend.justification = "right") +
  theme(legend.direction = "horizontal", legend.box = "vertical") 
```

>>>>

```{r}
p_subject <- ggplot(subject_all_years, aes(fct_reorder(description, n_oa / n, .fun = median), n_oa / n)) + 
  geom_boxplot(aes(color = subject_area)) +
  geom_jitter(alpha = .05, aes(color = subject_area), size = 1) +
  facet_wrap(~subject_area, scales = "free_y") +
  geom_hline(yintercept = median_all,  colour = "red", linetype ="dashed", size = 1) +
  scale_colour_manual(NULL, values = c("#7F3C8D", "#11A579", "#3969AC", "#F2B701"),
                      guide=FALSE) +
  scale_y_continuous(
    labels = scales::percent_format(accuracy = 5L),
    expand = expansion(mult = c(0, 0.05))
  ) +
  coord_flip(ylim=c(0,0.2)) +
  labs(x = NULL, y = "Five-Years OA Uptake Rate per Journal") +
  theme_minimal_vgrid(font_size = 10) 
ggsave(here::here("figure", "subject_by_area.png"), p_subject, dpi = 300, width = 8, height = 6)
p_subject
```

@@

```{r}
field_funder <- hybrid_df %>%
  filter(oa_sponsor_type == "FundingBody") %>%
  left_join(funder_codes, by = c("oa_sponsor_name" = "oa_sponsor")) %>%
  mutate(oa_sponsor = ifelse(is.na(oa_sponsor_short), "Other", oa_sponsor_short)) %>%
  mutate(oa_sponsor = fct_infreq(oa_sponsor)) %>%
  mutate(oa_sponsor = fct_lump_n(oa_sponsor, 10)) %>%
  left_join(jn_subjects, by = "issn") %>%
  filter(!is.na(top_level), top_level != "Multidisciplinary") %>%
  group_by(oa_sponsor, top_level) %>%
  summarise(n_oa_type = n_distinct(doi)) %>%
  mutate(prop = n_oa_type / sum(n_oa_type)) %>%
  mutate(oa_sponsor = fct_relevel(oa_sponsor, "Other", after = Inf))
# plot
pp <- ggplot(field_funder,
       aes(
         x = factor(oa_sponsor),
         y = reorder(top_level, desc(top_level)),
         colour = prop,
         size = n_oa_type
       )) +
  geom_point() +
  scale_color_viridis_c(
    labels = scales::percent_format(accuracy = 5L),
    option = "magma",
    name = "Percentage per funder",
    breaks =  scales::extended_breaks(),
    begin = 0.15,
    end = 0.85
  ) +
  scale_size("OA Articles") +
  scale_x_discrete(position = "top") +
  labs(x = NULL, y = NULL) +
  theme_minimal_grid(font_size = 10) +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_blank()
  ) +
  theme(legend.position = "top", legend.justification = "right") +
  theme(legend.direction = "horizontal", legend.box = "vertical") 
ggsave(here::here("figure", "funder_subject.png"), pp, dpi = 300, width = 8, height = 6)
```
